P2MS-ITB TEACHING FACTORY-NETWORK

### 2021-10-12 kampus merdeka/kurikulum.Rmd
draft

```{r,echo=FALSE}
met1 = c("Case-based learning",
	 "Problem-based learning",
	 "Challenge-based learning",
	 "Project-based learning",
	 "Experimental learning")
metode = data.frame(x = c("x","","","x",""),
	            y = met1)

metode %>%
  rename("Metode Pengajaran (pilih beberapa)" = y,
	 " " = x) %>%
  knitr::kable("simple",caption = "Teaching Methods")
```

>>>>

```{r,echo=FALSE}
met1 = c("Case-based learning",
	 "Problem-based learning",
	 "Challenge-based learning",
	 "Project-based learning",
	 "Experimental learning",
	 "",
	 "",
	 "")

met2 = c("Team-based learning",
	 "Collaborative team learning",
	 "Team learning",
	 "Lecture",
	 "Online learning",
	 "Debate",
	 "Concept Questions",
	 "Computational Lab Project (Colab)")

metode = data.frame(x1 = c("x","","","x","","","",""),
	            y1 = met1,
		    x2 = c("","","x","x","x","","",""),
		    y2 = met2)

metode %>%
  rename("Metode Pengajaran (pilih beberapa)" = y1,
	 " " = x1,
	 "Cara Penyampaian Materi" = y2,
	 "  " = x2) %>%
  knitr::kable("simple")
```

xxx
